---
title: "Prediction of Health Insurance Costs"
author: "Willy"
date: "24/2/2021"
output: html_document
---
```{r}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Description

The topic of the dataset that I chose in this post is about predicting health insurance costs. The dataset that I took is from Kaggle. There are four algorithms that I use, including Simple Linear Regression, Polynomial Regression, Multiple Linear Regression and Multiple Linear Regression with Interaction. To get the dataset, please click [here.](https://www.kaggle.com/mirichoi0218/insurance)

**Report Outline**:  
1. Data Extraction  
2. Exploratory Data Analysis (EDA)  
3. Remove Outliers  
4. Modelling  
5. Evaluate the Model  
6. Recomendation

## Load the Libraries

The following are the packages that need to be installed:

```{r}
library(tidyverse)
library(psych)
library(ggridges)
library(broom.mixed)
library(viridis)
library(modelr)
library(lme4)
library(patchwork)
```

## 1. Data Extraction

This dataset is downloaded from Kaggle and saved in the data folder. We use **read.csv()** function to read the dataset and **insurance_df** as a data frame.

```{r}
insurance_df <-  read.csv("C:/Users/lenovo/Documents/theprojectmine/data/insurance.csv")
```

## 1.1. Check for Missing Values

This section is a check whether there is a missing value or not.

```{r}
insurance_df %>%
  summarise_all(
    ~ sum(is.na(.))
  )
```

## 1.2. Change Target to Factor

This section represents any of the factors that affect the cost of health insurance.

```{r}
insurance_df <- insurance_df %>%
  mutate(sex = factor(sex),
         smoker = factor(smoker),
         region = factor(region),
         children = factor(children)
  )
```

## 2. Exploratory Data Analysis

### 2.1. Charges Variables

In this section, it is a variable part of health insurance costs.

```{r}
insurance_df %>%
  ggplot(aes(charges, ..density.., fill = I("#d45087"))) +
  geom_histogram(bins = 50) +
  geom_density()+
  theme(legend.position = "none")

tibble(low_charges = nrow(filter(insurance_df,charges<15000 )),
       middle_charges =  nrow(filter(insurance_df,charges>=15000 & charges<50000)),
       high_charges = nrow(filter(insurance_df, charges>=50000)),
)
```

### 2.2. Age Variables

In this section, it is a variable part of a person's age.

```{r}
insurance_df %>%
  ggplot(aes(age, fill = I("#d45087")))+
  geom_bar()+ 
  theme(legend.position = "none")

p1 <- insurance_df %>% 
  ggplot(aes(age, charges))+
  geom_point(color = I("#d45087"))

p2 <- insurance_df %>% 
  ggplot(aes(age, charges, color = smoker))+
  geom_point()

p1+p2
```

### 2.3. Sex Variables

In this section, it is part of the gender variable.

```{r}
p1 <- insurance_df %>%
  count(sex) %>% 
  ggplot(aes(sex, n, fill = I("#d45087")))+
  geom_col()+
  theme(legend.position = "none")

p2 <- insurance_df %>% 
  ggplot(aes(charges, sex, fill = sex)) +
  ggridges::geom_density_ridges()

p3 <- insurance_df %>% 
  ggplot(aes(sex, charges, fill = sex))+
  geom_boxplot()

(p1+p2)/p3
```

### 2.4. BMI Variables

In this section, is the variable part of body weight.

```{r}
p1 <- insurance_df %>%
  ggplot(aes(x = bmi, y = stat(density))) +
  geom_histogram( aes(fill = I("#d45087")), bins = 50) +
  theme(legend.position = "none") +
  geom_density()

p2 <- insurance_df %>% 
  ggplot(aes(x = bmi, charges, color = charges)) +
  geom_point() +
  scale_color_viridis(option = "E")

p3 <- insurance_df %>% 
  ggplot(aes(factor(age), bmi, color = I("#d45087"))) +
  geom_point() +
  geom_jitter() +
  stat_summary(fun = mean, colour = "blue", geom = "point", size = 5)

(p1+p2)/p3
```

### 2.5. The Number of Children

In this section, it is a variable part of the number of children of that person.

```{r}
p1 <- insurance_df %>%
  count(children) %>% 
  ggplot(aes(children, n))+
  geom_col( aes(fill = I("#d45087")))+
  theme(legend.position = "none")

p2 <- insurance_df %>% 
  ggplot(aes(children, charges, fill = children))+
  geom_boxplot()

p1+p2
```

### 2.6. Smoker Variables

In this section, it is a variable part of whether the person smokes or not.

```{r}
p1 <- insurance_df %>%
  ggplot(aes(smoker,charges, fill = smoker))+
  geom_boxplot()

p2 <- insurance_df %>%
  ggplot(aes(charges, fill = smoker, alpha = 0.5))+
  geom_density()

p1/p2
```

### 2.7. Region Variables

In this section, it is a variable part based on where the person lives.

```{r}
p1 <- insurance_df %>%
  count(region) %>% 
  ggplot(aes(region, n, width = 0.7, fill = I("#d45087")))+
  geom_col()+
  coord_flip()+
  theme(legend.position = "none")

p2 <- insurance_df %>% 
  ggplot(aes(charges, region, fill = region)) +
  ggridges::geom_density_ridges()

p3 <- insurance_df %>% 
  ggplot(aes(region, charges, fill = region))+
  geom_boxplot()+
  coord_flip()

p1+(p2/p3)
```

## 3. Remove Outliers

### 3.1. Get Outliers Values

In this section, it is a part of getting the outliers value.

```{r}
outliers_charges <- boxplot.stats(insurance_df$charges)$out
outliers_charges
```

### 3.2. Get Index of Outliers

In this section, it is part of getting the index from the outliers.

```{r}
outliers_ind <- which(insurance_df$charges %in% c(outliers_charges))
outliers_ind
```

### 3.3. Data With Outliers

In this section, is the part using data with outliers.

```{r}
outliers_data <- insurance_df[outliers_ind, ]
insurance_df[outliers_ind, ]
```

### 3.4. Data Without Outliers

In this section, it is a part of using data without outliers.

```{r}
insurance_df[-outliers_ind, ]
insurance_df_no <- insurance_df[-outliers_ind,]
```

### 3.5 One Hot Encoder

In this section, it is one hot encoder.

```{r}
library(caret)
dmy = dummyVars(" ~ .", data = insurance_df_no[, -7])
encode_df = data.frame(predict(dmy, newdata = insurance_df_no[, -7]))
encode_df$charges <- insurance_df_no$charges
```

### 3.6. Divide Data Into Train and Test

This section is dividing the data into two, namely train and test.

```{r}
m <- nrow(insurance_df_no)
set.seed(2021)
train_idx <- sample(m, m * 0.8)

train_df <- insurance_df_no[train_idx, ]
test_df <- insurance_df_no[-train_idx, ]
```

## 4. Modelling

### 4.1. Simple Linear Regression

This section uses Simple Linear Regression.

```{r}
fit.linreg <- lm(charges ~ smoker+age+bmi+children+region, data = train_df)
summary(fit.linreg)
```

### 4.2. Polynomial Regression

This section uses Polynomial Regression.

```{r}
fit.polyreg <- lm(charges ~ smoker+age+bmi+children+region+I(age^2)+I(bmi^2), data = train_df)
summary(fit.polyreg)
```

### 4.3. Multiple Linear Regression

This section uses Multiple Linear Regression.

```{r}
fit.multireg <- lm(formula = charges ~ ., data = train_df)
summary(fit.multireg)
```

### 4.4. Multiple Linear Regression with Interaction

This section uses Multiple Linear Regression with Interaction.

```{r}
fit.inmultireg <- lm(charges ~ smoker+age+bmi+children+region+I(age^2)+I(bmi^2)+age:bmi, data = train_df)
summary(fit.inmultireg)
```

## 5. Evaluate the Model

This section evaluates the computational results of several types of regression models.

```{r}
performance = function(test_df, model, model_name) {
  
  pred <- predict(model, test_df)
  error <- pred - test_df$charges
  mse <- mean(error ^ 2)
  rmse <- sqrt(mse)
  
  result <- paste("RMSE of", model_name, ":",
                  round(rmse, 2))
  result
}

performance(test_df, fit.linreg, "Simple Linear Regression")
performance(test_df, fit.polyreg, "Polynomial Regression")
performance(test_df, fit.multireg, "Multiple Linear Regression")
performance(test_df, fit.inmultireg, "MLR with Interaction")
```

### 5.1. Scatterplot

For this section, display a graph of the error count results of the four different types of regression models.

```{r}
fit.inmultireg <- lm(charges ~ smoker+age+bmi+children+region+I(age^2)+I(bmi^2)+age:bmi, data = train_df)
summary(fit.inmultireg)
```

## 6. Recommendation

1. Of the four types of regression models we use, the smaller error count is 4476.75 (Polynomial Regression).
2. Factors that influence the cost of health insurance are weight, age, smoking and gender.
3. Based on the results of the graph, the prediction of health insurance costs is below 20,000.